Hector Permafrost

### 2019-06-03 analysis/paper/paper.Rmd
Add biome simulation figures

>>>>

## Global Hector

```{r fig-global-timeseries, fig.cap = global_ts_cap, fig.dim = c(10, 8)}
global_ts_cap <- paste(
  "Time series of Hector outputs for different parameter combinations."
)
readd(ts_global_sims)
```

```{r fig-global-scatter, fig.cap = global_scatter_cap, fig.dim = c(8, 5)}
global_scatter_cap <- paste(
  "Hector outputs at 2100 as a function of input parameter values."
)
readd(scatter_lastyear_global_sims)
```

```{r fig-global-sensitivity, fig.cap = global_sensitivity_cap, fig.dim = c(5, 5)}
global_sensitivity_cap <- paste(
  "Sensitivity and variance decomposition analysis for global Hector."
)
readd(sensitivity_plot_sensitivity_global_params_lastyear_global_sims)
```

## Permafrost as a biome

```{r fig-biome-timeseries, fig.cap = biome_ts_cap, fig.dim = c(10, 8)}
biome_ts_cap <- paste(
  "Overall parameter uncertainty of Hector simulations with permafrost biome."
)
readd(ts_biome_sims)
```

```{r fig-biome-scatter, fig.cap = biome_scatter_cap, fig.dim = c(8, 8)}
biome_scatter_cap <- paste(
  "Hector outputs (with permafrost biome) at 2100 as a function of input parameter values."
)
readd(scatter_lastyear_biome_sims)
```

```{r fig-biome-sensitivity, fig.cap = biome_sensitivity_cap, fig.dim = c(5, 7)}
biome_sensitivity_cap <- paste(
  "Sensitivity and variance decomposition analysis for Hector with permafrost biome."
)
readd(sensitivity_plot_sensitivity_biome_params_lastyear_biome_sims)
```

## Permafrost methane emissions
